Synthesizing by means of mice

### 2020-07-27 mice_synthesizing/Mice_Synthesizing.Rmd
Alter cart settings for better bias/variance tradeoff (more variance, less bias)

```{r, message = F}
synthetic_results <- boot_cart %>%
  map(function(x) x %$% lm(wgt ~ age + hgt)) %>%
  map_dfr(pool.syn) %>%
  ci_cov(truemodel) %>%
  kable(digits = 3) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

@@

true_results <- bootstrap_boys %>%
  map(~ lm(wgt ~ age + hgt, .x)) %>%
  map_dfr(~ broom::tidy(.x, conf.int = TRUE)) %>%
  mutate(true_coef = rep(coef(truemodel), nsim),
         true_se   = rep(sqrt(diag(vcov(truemodel))), nsim),
         cover     = conf.low < true_coef & true_coef < conf.high) %>%
  group_by(term) %>%
  summarise("True Est" = unique(true_coef),
            "Boot Est"  = mean(estimate),
            "Bias"     = mean(estimate - true_coef),
            "True SE"  = unique(true_se),
            "Boot SE"   = mean(std.error),
            "DF"       = 745,
            "Lower"    = mean(conf.low),
            "Upper"    = mean(conf.high),
            "CIW"      = mean(conf.high - conf.low),
            "Coverage" = mean(cover)) %>%
  kable(digits = 3) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

@@

```{r, echo = F}
true_results
synthetic_results
norm_results

>>>>

```{r, message = F}
synthetic_results <- boot_cart %>%
  map(function(x) x %$% lm(wgt ~ age + hgt)) %>%
  map_dfr(pool.syn) %T>% 
  assign("boot_syn", ., envir = globalenv()) %>%
  ci_cov(truemodel) %>%
  kable(digits = 3) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

@@

true_results <- bootstrap_boys %>%
  map(~ lm(wgt ~ age + hgt, .x)) %>%
  map_dfr(~ broom::tidy(.x, conf.int = TRUE)) %>%
  mutate(true_coef = rep(coef(truemodel), nsim),
         true_se   = rep(sqrt(diag(vcov(truemodel))), nsim),
         cover     = conf.low < true_coef & true_coef < conf.high) %T>% 
  assign("boot_true", ., envir = globalenv()) %>%
  group_by(term) %>%
  summarise("True Est" = unique(true_coef),
            "Boot Est"  = mean(estimate),
            "Bias"     = mean(estimate - true_coef),
            "True SE"  = unique(true_se),
            "Boot SE"   = mean(std.error),
            "DF"       = 745,
            "Lower"    = mean(conf.low),
            "Upper"    = mean(conf.high),
            "CIW"      = mean(conf.high - conf.low),
            "Coverage" = mean(cover)) %>%
  kable(digits = 3) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

@@

```{r, echo = F}
true_results
synthetic_results
norm_results
```

We find that some bias has been introduced due to synthesizing the relationships, so we investigate this in further depth. Additionally, the coverage is somewhat too high, and the average confidence interval width has increased dramatically. Therefore, we will further investigate where this increase stems from.

```{r, message = F, fig.fullwidth = TRUE, dpi = 1000}
plot_dat <- bind_rows("Synthetic" = boot_syn %>% 
                                    mutate(ciw = upper - lower) %>%
                                    select(term, est, ciw = ciw), 
                      "Real values" = boot_true %>% 
                                      mutate(ciw = conf.high - conf.low) %>%
                                      select(term, est = estimate, ciw = ciw),
                      .id = "Method")

ggplot(plot_dat, aes(x = est, color = Method, fill = Method)) +
  geom_density(alpha = .7) +
  facet_wrap(~ term, nrow = 1, scales = "free") +
  scale_color_viridis_d(begin = .30, end = .65) +
  scale_fill_viridis_d(begin = .30, end = .65) +
  theme_classic()
```

It can be seen that the bias is systematic, and thus not due to any extreme values that pull the average estimate to zero. Additionally, it seems that the pooled standard error indicated in the table is somewhat too low for the synthetic data. Namely, it appears in the plot that the spread in the synthetic data is roughly equal to the spread in the bootstrapped, but real, data. However, in the table above, the synthetic standard errors are much smaller than the mean over the manually calculated standard error of the bootstrapped estimates. When the standard errors are calculated over the obtained regression estimates, we find that the synthetic standard error increases much more when we calculate it over the observed synthetic estimates.

```{r, message = F}
boot_se <- boot_true %>% group_by(term) %>% summarise("Bootstrapped SE" = sd(estimate))
boot_syn_se <- boot_syn %>% group_by(term) %>% summarise("Synthetic bootstrapped SE" = sd(est))

bind_cols(boot_se, boot_syn_se[,2]) %>%
  kable(digits = 3) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"),
                full_width = FALSE)
```

```{r, fig.fullwidth = TRUE, dpi = 1000}
ggplot(plot_dat, aes(x = ciw, color = Method, fill = Method)) +
  geom_density(alpha = .7) +
  facet_wrap(~ term, nrow = 1, scales = "free") +
  scale_color_viridis_d(begin = .30, end = .65) +
  scale_fill_viridis_d(begin = .30, end = .65) +
  theme_classic()
```

When we look at the confidence interval width, we find that the bootstrap CI is of approximately the same length in all iterations, while the CI's of the synthetic results spread out much more.
